---
title: "Question 1"
description: |
  Vast Challenge 2022-Question 1
author:
  - name: Bomin Kim 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Reading packages

```{r}
packages = c('sf', 'tmap', 'tidyverse', 
             'lubridate', 'clock', 
             'sftime', 'rmarkdown', "binr","ggplot2","ggpubr")
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

```{r}

buildings <- read_sf("data/Buildings.csv", 
                     options = "GEOM_POSSIBLE_NAMES=location")
apartments <- read_sf("data/Apartments.csv", 
                      options = "GEOM_POSSIBLE_NAMES=location")
participants <- read_rds("data/hw2_participants.rds")
apartments_1 <- readRDS("data/apartments_1.rds")
buildingsshx<-st_read("data/buildings.shx")
```

# 1. Building Type 
# interactive base map 

```{r}
buildings<-st_join(buildings,buildingsshx%>%
                      select(region)%>%
                mutate(region=as.character(region)),by=c("buildingId"="bldngId"))

tmap_mode("view")
tm_shape(buildings)+
  tm_polygons(col = "buildingType",
              size = 1,
              title = "Building Type",
              border.col = "black",
              border.lwd = 1) +
  tm_layout(main.title= 'Building Type in Engagement, Ohio', 
            main.title.position = c('left'),
            main.title.size = 1.3, legend.outside = TRUE,)
```

# Static 4*tmap

```{r}
buildings_c<-buildings%>%
  filter(region=="Central")
buildings_s<-buildings%>%
  filter(region=="South")
buildings_e<-buildings%>%
  filter(region=="East")
buildings_nw<-buildings%>%
  filter(region=="North-west")

tmap_mode("plot")
tm_shape(buildings_c)+
  tm_polygons(col = "buildingType",
              size = 1,
              title = "Building Type",
              border.col = "black",
              border.lwd = 1) +
  tm_layout(main.title= 'Building Type in Central Engagement, Ohio', 
            main.title.position = c('left'),
            main.title.size = 1.3, legend.outside = TRUE,)

tm_shape(buildings_s)+
  tm_polygons(col = "buildingType",
              size = 1,
              title = "Building Type",
              border.col = "black",
              border.lwd = 1) +
  tm_layout(main.title= 'Building Type in South Engagement, Ohio', 
            main.title.position = c('left'),
            main.title.size = 1.3, legend.outside = TRUE,)

tm_shape(buildings_e)+
  tm_polygons(col = "buildingType",
              size = 1,
              title = "Building Type",
              border.col = "black",
              border.lwd = 1) +
  tm_layout(main.title= 'Building Type in East Engagement, Ohio', 
            main.title.position = c('left'),
            main.title.size = 1.3, legend.outside = TRUE,)

tm_shape(buildings_nw)+
  tm_polygons(col = "buildingType",
              size = 1,
              title = "Building Type",
              border.col = "black",
              border.lwd = 1) +
  tm_layout(main.title= 'Building Type in Northwest Engagement, Ohio', 
            main.title.position = c('left'),
            main.title.size = 1.3, legend.outside = TRUE,)
```

# Bar chart

```{r}
buildings1<-as.data.frame(buildings)
split<-buildings1%>%group_by(region,buildingType)%>%summarise(number=n())

ggplot(split,aes(x=factor(region,
                  levels=c("Central","East","North-west","South")),
                 y=number,fill=buildingType))+
  geom_col()+
    ggtitle("Building Type in Engagement, Ohio")+
  theme(plot.title = element_text(hjust = 0.5))
```

# 2. Population density 
# Interactive base map 

```{r}
apartments <- apartments %>%
  select(c("apartmentId", "buildingId","rentalCost")) %>%
  rename("venueId" = "apartmentId") 
apartments$venueId <- as.numeric(as.character(apartments$venueId))
apartments$buildingtype <- "Apartment"

apartments_2<-apartments_1%>%
  group_by(buildingId)%>%
  summarise(density=n())

apartmentoccupancy<-left_join(buildings,
                              apartments_2%>%
                               mutate(buildingId=as.character(buildingId)),
                             by=c("buildingId"="buildingId"))


tmap_mode("view")
tm_shape(apartmentoccupancy)+
  tm_polygons(col = "density",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Population density in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# Static 4*tmap

```{r}
apartmentoccupancy_c<-apartmentoccupancy%>%
  filter(region=="Central")
apartmentoccupancy_s<-apartmentoccupancy%>%
  filter(region=="South")
apartmentoccupancy_e<-apartmentoccupancy%>%
  filter(region=="East")
apartmentoccupancy_nw<-apartmentoccupancy%>%
  filter(region=="North-west")

tmap_mode("plot")
tm_shape(apartmentoccupancy_c)+
  tm_polygons(col = "density",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Population density in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancy_s)+
  tm_polygons(col = "density",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Population density in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancy_e)+
  tm_polygons(col = "density",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Population density in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancy_nw)+
  tm_polygons(col = "density",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Population density in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# Bar chart

```{r}
apartmentoccupancy1<-as.data.frame(apartmentoccupancy)
apartmentoccupancysplit<-apartmentoccupancy1%>%group_by(region)%>%
  summarise(number=n())

ggplot(apartmentoccupancysplit,aes(x=factor(region,
                  levels=c("Central","East","North-west","South")),
                 y=number))+
  geom_col()+
    ggtitle("Population in Engagement, Ohio")+
  theme(plot.title = element_text(hjust = 0.5))
```

# 3. Age group density 
# Interactive base map 

```{r}
apartments_age<-merge(apartments_1,participants[,c("participantId","agegroup")],by="participantId",all.x=TRUE)
apartments_age<-apartments_age%>%
  group_by(agegroup,buildingId)%>%
  summarise(density=n())

apartmentoccupancyage<-left_join(buildings,
                              apartments_age%>%
                                mutate(buildingId=as.character(buildingId)),
                              by=c("buildingId"="buildingId"))
#apartmentoccupancyage<-na.omit(apartmentoccupancyage)

tmap_mode("view")
tm_shape(apartmentoccupancyage)+
  tm_polygons(col = "agegroup",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by age group in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
tmap_mode("plot")
```

# 4*tmap

```{r}
apartmentoccupancyage_c<-apartmentoccupancyage%>%
    filter(region=="Central")
apartmentoccupancyage_e<-apartmentoccupancyage%>%
    filter(region=="East")
apartmentoccupancyage_nw<-apartmentoccupancyage%>%
    filter(region=="North-west")
apartmentoccupancyage_s<-apartmentoccupancyage%>%
    filter(region=="South")

tmap_mode("plot")
tm_shape(apartmentoccupancyage_c)+
  tm_polygons(col = "agegroup",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by age group in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyage_e)+
  tm_polygons(col = "agegroup",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by age group in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyage_nw)+
  tm_polygons(col = "agegroup",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by age group in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyage_s)+
  tm_polygons(col = "agegroup",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by age group in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

```

# Bar chart

```{r}
apartmentoccupancyage1<-na.omit(apartmentoccupancyage)
apartmentoccupancyage1<-as.data.frame(apartmentoccupancyage1)
apartmentoccupancyagesplit<-apartmentoccupancyage1%>%group_by(region,agegroup)%>%summarise(number=n())

ggplot(apartmentoccupancyagesplit,aes(x=factor(region,
                  levels=c("Central","East","North-west","South")),
                 y=number,fill=agegroup))+
  geom_col()+
    ggtitle("Density by age group in Engagement, Ohio")+
  theme(plot.title = element_text(hjust = 0.5))
```

# 4. Income Level 
# Interactive base map 

```{r}
apartments_income<-merge(apartments_1,participants[,c("participantId","wage")],by="participantId",all.x=TRUE)

apartmentoccupancyincome<-left_join(buildings,
                              apartments_income%>%
                                mutate(buildingId=as.character(buildingId)),
                              by=c("buildingId"="buildingId"))
tmap_mode("view")
tm_shape(apartmentoccupancyincome)+
  tm_polygons(col = "wage",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by income in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# 4*tmap

```{r}
apartmentoccupancyincome_c<-apartmentoccupancyincome%>%
    filter(region=="Central")
apartmentoccupancyincome_e<-apartmentoccupancyincome%>%
    filter(region=="East")
apartmentoccupancyincome_nw<-apartmentoccupancyincome%>%
    filter(region=="North-west")
apartmentoccupancyincome_s<-apartmentoccupancyincome%>%
    filter(region=="South")

tmap_mode("plot")
tm_shape(apartmentoccupancyincome_c)+
  tm_polygons(col = "wage",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by income in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyincome_e)+
  tm_polygons(col = "wage",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by income in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyincome_nw)+
  tm_polygons(col = "wage",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by income in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyincome_s)+
  tm_polygons(col = "wage",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by income in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

```

# Bar chart

```{r}
apartmentoccupancyincome1<-na.omit(apartmentoccupancyincome)
apartmentoccupancyincome1<-as.data.frame(apartmentoccupancyincome1)

ggplot(apartmentoccupancyincome1,aes(y = wage,x= region)) +
    geom_violin(fill="light blue") +
    geom_boxplot(alpha=0.5) + 
    stat_summary(geom = "point", fun.y="mean", colour ="red",size=2) +
    ggtitle("Density by income in Engagement, Ohio")+
    theme(plot.title = element_text(hjust = 0.5))

```

# 5.Kids
# Interactive map

```{r}
apartments_kids<-merge(apartments_1,participants[,c("participantId","haveKids")],by="participantId",all.x=TRUE)

apartmentoccupancykids<-left_join(buildings,
                              apartments_kids%>%
                                mutate(buildingId=as.character(buildingId)),
                              by=c("buildingId"="buildingId"))
tmap_mode("view")
tm_shape(apartmentoccupancykids)+
  tm_polygons(col = "haveKids",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by having kids in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# 4*tmap

```{r}
apartmentoccupancykids_c<-apartmentoccupancykids%>%
    filter(region=="Central")
apartmentoccupancykids_e<-apartmentoccupancykids%>%
    filter(region=="East")
apartmentoccupancykids_nw<-apartmentoccupancykids%>%
    filter(region=="North-west")
apartmentoccupancykids_s<-apartmentoccupancykids%>%
    filter(region=="South")

tmap_mode("plot")
tm_shape(apartmentoccupancykids_c)+
  tm_polygons(col = "haveKids",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by having kids in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancykids_e)+
  tm_polygons(col = "haveKids",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by having kids in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancykids_nw)+
  tm_polygons(col = "haveKids",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by having kids in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancykids_s)+
  tm_polygons(col = "haveKids",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by having kids in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# chart

```{r}
apartmentoccupancykids1<-na.omit(apartmentoccupancykids)
apartmentoccupancykids1<-as.data.frame(apartmentoccupancykids1)
apartmentoccupancykidsplit<-apartmentoccupancykids1%>%group_by(region,haveKids)%>%summarise(number=n())

ggplot(apartmentoccupancykidsplit,aes(x=factor(region,
                  levels=c("Central","East","North-west","South")),
                 y=number,fill=haveKids))+
  geom_col()+
    ggtitle("Density by having kids in Engagement, Ohio")+
  theme(plot.title = element_text(hjust = 0.5))
```

# 6.Rental Cost 
# Interactive base map 

```{r}
apartments_rental<-left_join(buildings,
                              apartments_1%>%
                                mutate(buildingId=as.character(buildingId)),
                              by=c("buildingId"="buildingId"))
apartments_rental <- apartments_rental %>% 
  mutate(internval = cut(as.numeric(rentalCost), 
                      breaks = c(0, 300, 600, 900,+Inf),
                      labels = c("0-300", "300-600", "600-900", "900+")))
tmap_mode("view")
tm_shape(apartments_rental)+
  tm_fill("internval",title = "Monthly rent",palette = "Blues")+
  tm_polygons(col = "rentalCost",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by Rental Cost in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# 4*tmap

```{r}
apartments_rental_c<-apartments_rental%>%
    filter(region=="Central")
apartments_rental_e<-apartments_rental%>%
    filter(region=="East")
apartments_rental_nw<-apartments_rental%>%
    filter(region=="North-west")
apartments_rental_s<-apartments_rental%>%
    filter(region=="South")

tmap_mode("plot")
tm_shape(apartments_rental_c)+
  tm_polygons(col = "rentalCost",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by Rental Cost in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartments_rental_e)+
  tm_polygons(col = "rentalCost",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by Rental Cost in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartments_rental_nw)+
  tm_polygons(col = "rentalCost",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by Rental Cost in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartments_rental_s)+
  tm_polygons(col = "rentalCost",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by Rental Cost in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# Chart

```{r}
apartments_rental1_c<-na.omit(apartments_rental_c)
apartments_rental1_c<-as.data.frame(apartments_rental1_c)
apartments_rental1_c$rentalCost<-as.numeric(apartments_rental1_c$rentalCost)
apartments_rental1_e<-na.omit(apartments_rental_e)
apartments_rental1_e<-as.data.frame(apartments_rental1_e)
apartments_rental1_e$rentalCost<-as.numeric(apartments_rental1_e$rentalCost)
apartments_rental1_nw<-na.omit(apartments_rental_nw)
apartments_rental1_nw<-as.data.frame(apartments_rental1_nw)
apartments_rental1_nw$rentalCost<-as.numeric(apartments_rental1_nw$rentalCost)
apartments_rental1_s<-na.omit(apartments_rental_s)
apartments_rental1_s<-as.data.frame(apartments_rental1_s)
apartments_rental1_s$rentalCost<-as.numeric(apartments_rental1_s$rentalCost)

p1<-ggplot(apartments_rental1_c,aes(rentalCost))+
  geom_histogram(bins=(max(apartments_rental1_c$rentalCost)-min(apartments_rental1_c$rentalCost))/30,
                 color="blue",fill="blue")+
  ggtitle("Rental Cost in Central Engagement")+
  xlab("Rent")+ylab("# of Aparments")+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(data=apartments_rental1_c, aes(xintercept=mean(apartments_rental1_c$rentalCost), color="red"),
             linetype="dashed",show.legend = F)

p2<-ggplot(apartments_rental1_e,aes(rentalCost))+
  geom_histogram(bins=(max(apartments_rental1_c$rentalCost)-min(apartments_rental1_c$rentalCost))/30,
                 color="blue",fill="blue")+
  ggtitle("Rental Cost in East Engagement")+
  xlab("Rent")+ylab("# of Aparments")+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(data=apartments_rental1_e, aes(xintercept=mean(apartments_rental1_e$rentalCost), color="red"),
             linetype="dashed",show.legend = F)

p3<-ggplot(apartments_rental1_nw,aes(rentalCost))+
  geom_histogram(bins=(max(apartments_rental1_c$rentalCost)-min(apartments_rental1_c$rentalCost))/30,
                 color="blue",fill="blue")+
  ggtitle("Rental Cost in Northwest Engagement")+
  xlab("Rent")+ylab("# of Aparments")+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(data=apartments_rental1_nw, aes(xintercept=mean(apartments_rental1_nw$rentalCost), color="red"),
             linetype="dashed",show.legend = F)

p4<-ggplot(apartments_rental1_s,aes(rentalCost))+
  geom_histogram(bins=(max(apartments_rental1_c$rentalCost)-min(apartments_rental1_c$rentalCost))/30,
                 color="blue",fill="blue")+
  ggtitle("Rental Cost in South Engagement")+
  xlab("Rent")+ylab("# of Aparments")+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(data=apartments_rental1_s, aes(xintercept=mean(apartments_rental1_s$rentalCost), color="red"),
             linetype="dashed",show.legend = F)

ggarrange(p1, p2, p3, p4,
          ncol = 2, nrow = 2)




```

# 7. Joviality
# Interactive base map 

```{r}
apartments_joviality<-merge(apartments_1,participants[,c("participantId","joviality")],by="participantId",all.x=TRUE)

apartmentoccupancyjoviality<-left_join(buildings,
                              apartments_joviality%>%
                                mutate(buildingId=as.character(buildingId)),
                              by=c("buildingId"="buildingId"))
tmap_mode("view")
tm_shape(apartmentoccupancyjoviality)+
  tm_polygons(col = "joviality",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by joviality in Engagement, Ohio",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# 4*tmap

```{r}
apartmentoccupancyjoviality_c<-apartmentoccupancyjoviality%>%
    filter(region=="Central")
apartmentoccupancyjoviality_e<-apartmentoccupancyjoviality%>%
    filter(region=="East")
apartmentoccupancyjoviality_nw<-apartmentoccupancyjoviality%>%
    filter(region=="North-west")
apartmentoccupancyjoviality_s<-apartmentoccupancyjoviality%>%
    filter(region=="South")

tmap_mode("plot")
tm_shape(apartmentoccupancyjoviality_c)+
  tm_polygons(col = "joviality",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by joviality in Central",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyjoviality_e)+
  tm_polygons(col = "joviality",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by joviality in East",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyjoviality_nw)+
  tm_polygons(col = "joviality",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by joviality in Northwest",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()

tm_shape(apartmentoccupancyjoviality_s)+
  tm_polygons(col = "joviality",
              border.col = "grey",
              style="cont",
              palette = "Blues",
              border.lwd = 1,
              border.alpha = 0.5,
              colorNA = "white")+
  tm_layout(frame=F,
            main.title = "Density by joviality in South",
            main.title.size = 1,
            legend.position = c("right","top"),
            legend.height = 0.2,
            legend.width = 0.2)+
  tm_compass()
```

# Chart

```{r}
apartmentoccupancyjoviality1<-na.omit(apartmentoccupancyjoviality)
apartmentoccupancyjoviality1<-as.data.frame(apartmentoccupancyjoviality1)
apartmentoccupancyjovialityplit<-apartmentoccupancyjoviality1%>%group_by(region,joviality)%>%summarise(number=n())

ggplot(apartmentoccupancyjoviality1,aes(y = joviality,x= region)) +
    geom_violin(fill="light blue") +
    geom_boxplot(alpha=0.5) + 
    stat_summary(geom = "point", fun.y="mean", colour ="red",size=2) +
    ggtitle("Density by joviality in Engagement, Ohio")+
    theme(plot.title = element_text(hjust = 0.5))
```


